Questions regarding modeling

### 2020-09-30 Questions.Rmd
updated Questions

@@

@@

@@

>>>>

    * Right, there are many different prior choices. In general, the choice of prior is not that important. You can also check the posterior distribution and compare with the prior to explore how sensitive the model is to the prior choice.

@@

* The model we are fitting is very similar. The primary difference is that our model can be expressed as $y_n \sim normal(\alpha+\beta f(x_n),\sigma)$ where $f(x_n)$ is a function of the $x_n$. In the model above, $f(x_n) = x_n$ is the identity function whereas in the `time-varying.stan` model we use the b-spline function $f(\cdot)$.

@@

* The $X_{bs}$ is the transformation of $X$ by the function $f(X)$. There are lots of functions $f(\cdot)$ that are widely used (log transformations, square roots, polynomials etc.). For example, $y_n \sim normal(\alpha+\beta_1 x_n + \beta_2 x_n^2, \sigma)$ is a function $f(x_n) = x_n + x_n^2$. The function $f(\cdot)$ is deterministic which means that the random seed should not matter.

@@

* The model defines $\mu$ as a matrix where each row represents a treatment and each column represents a time step. Thus, $\mu[2, 4]$ is the mean response for treatment 2 at during the 4th time period. The basis functions in $X_{bs}$ allow for the time-varying process to be different for each treatment (each row of $\beta$ are the parameters for a treatment). The $X_{bs} \beta$ model the correlation in the $y$ variable over time based on how close in time the observations are.
